---
title: "Final project"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

Import all library
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggcorrplot) # install.packages("ggcorrplot")
library(ggpubr)
library(ggmap)
########### data_dict ########### 
data_dict <- function(data, print_table = "No"){
  # packages
  suppressPackageStartupMessages(suppressWarnings(require(tidyverse)))
  suppressPackageStartupMessages(suppressWarnings(require(psych)))
  suppressPackageStartupMessages(suppressWarnings(require(ggpubr)))
  suppressPackageStartupMessages(suppressWarnings(require(gridExtra)))
  # get rid of scientific notation
  options(scipen = 999)
  # Get variable info and NAs
  var_info <- data.frame(Variable = names(data),
                         VariableType = sapply(data, class),
                         MissingValues = sapply(data, function(y) 
                           sum(length(which(is.na(y))))),
                         row.names = NULL)
  # get descriptive stats
  desc_stats <- data.frame(Variable = names(data), 
                           describe(data)[c(2:5, 13, 8:10)], 
                           row.names = NULL)
  # Create the data dictionary
  d_dict <- merge(var_info, desc_stats, by = "Variable")
  d_dict <- d_dict %>% mutate_at(vars("mean":"range"), .fun = round, 2)
  # NA's for summary stats of variables not of class numeric or integer
  d_dict <- d_dict %>%
    mutate(mean = ifelse(VariableType == "numeric" | VariableType == "integer", mean, ""),
           sd = ifelse(VariableType == "numeric" | VariableType == "integer", sd, ""),
           median = ifelse(VariableType == "numeric" | VariableType == "integer", median, ""),
           se = ifelse(VariableType == "numeric" | VariableType == "integer", se, ""),
           min = ifelse(VariableType == "numeric" | VariableType == "integer", min, ""),
           max = ifelse(VariableType == "numeric" | VariableType == "integer", max, ""),
           range = ifelse(VariableType == "numeric" | VariableType == "integer", range, ""))
  # return the result
  if(print_table == "No"){
    return(d_dict)
  } else {
    #create table if table = TRUE
    d_dict <- ggtexttable(d_dict,
                          rows = NULL)
    return(d_dict)
  }
}

########### summarize_numeric ########### 
summarize_numeric = function(dataset) {

  dataset = select_if(dataset, is.numeric)
  summary.table = data.frame(Attribute = names(dataset))

  summary.table = summary.table %>%
    mutate('Missing Values' = apply(dataset, 2, function (x) sum(is.na(x))),
           'Unique Values' = apply(dataset, 2, function (x) length(unique(x))),
           'Mean' = colMeans(dataset, na.rm = TRUE),
           'Min' = apply(dataset, 2, function (x) min(x, na.rm = TRUE)),
           'Max' = apply(dataset, 2, function (x) max(x, na.rm = TRUE)),
           'SD' = apply(dataset, 2, function (x) sd(x, na.rm = TRUE))
    )
  summary.table
}
```

Import data
```{r}
final_data = as_tibble(read.csv("./data/all_data_v3.csv"))
```

4.1 Check missing values
```{r}
# Data overview
data_dict(final_data, print_table = 'Yes')
```
4.2 
```{r}
distinct(final_data, room_type)
distinct(final_data, neighbourhood_group)
distinct(final_data, neighbourhood)
```

crime incidnet
```{r}
n1 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=crime_incidents_count))
n2 = ggplot(final_data) + geom_boxplot(aes(x=neighbourhood_group, y=crime_incidents_count))
ggarrange(n1, n2, ncol=3)
```

4.3.1.	Univariate Summary of Factors
```{r}
# summary(final_data)
colnames(final_data %>% select_if((is.character)))
g1 = ggplot(final_data) + geom_bar(aes(x=room_type))
g2 = ggplot(final_data) + geom_bar(aes(x=neighbourhood_group))
g3 = ggplot(final_data) + geom_bar(aes(x=neighbourhood))
ggarrange(g1, g2, g3)
ggarrange(g1, g3, nrow=2)
```

4.3.2.	Explore Numeric Attributes
```{r}
####### plot all #########
colnames(final_data %>% select_if((is.numeric)))
n1 = ggplot(final_data) + geom_histogram(aes(x=price))
n2 = ggplot(final_data) + geom_histogram(aes(x=availability_365))
n3 = ggplot(final_data) + geom_histogram(aes(x=avg_rating))
n4 = ggplot(final_data) + geom_histogram(aes(x=crime_level))
n5 = ggplot(final_data) + geom_histogram(aes(x=crime_incidents_count))
ggarrange(n1, n2, n3, n4, n5, ncol=5, nrow=1)
ggarrange(g1, g3, nrow=2)

####### mean min max SD #########
numeric_data = final_data %>% select(price, availability_365, avg_rating, crime_level, crime_incidents_count)
summarize_numeric(numeric_data)
```

Summary of Attributes After Initial Analysis
convert price into unit price (price/room_type)
```{r}
# 4, 2, 1, 1
# final_data = final_data %>%
#   mutate(unit_price = ifelse(room_type=='Entire home/apt',price/4,ifelse(room_type=='Hotel room',price/2,price)))
# 4, 2, 2, 1
final_data = final_data %>%
  mutate(unit_price = ifelse(room_type=='Entire home/apt',price/4,ifelse(room_type=='Shared room',price,price/2)))
```

plot unit price: EDA - Bivariate Analysis (Measures)
```{r}
####### plot all #########

ggplot(final_data) + geom_histogram(aes(x=unit_price), bins=100)
ggplot(final_data) + geom_bar(aes(x=unit_price))

####### mean min max SD #########
numeric_data = final_data %>% select(unit_price, avg_rating, crime_level, crime_incidents_count)
summarize_numeric(numeric_data)
```

Bivariate Analysis - Correlation matrix
```{r}
cor_data = select(final_data, c(unit_price, avg_rating, crime_level, crime_incidents_count))
fullCorrMatrix = round(cor(cor_data %>% select_if(is.numeric)), 2)
ggcorrplot(fullCorrMatrix, lab = TRUE)
```
EDA - Bivariate Analysis (Measures)
```{r}
# unit_price vs avg_rating
ggplot(final_data) + geom_point(aes(x=avg_rating, y=unit_price))
# unit_price vs crime_level
ggplot(final_data) + geom_point(aes(x=crime_level, y=unit_price))
# unit_price vs crime_incidents_count
ggplot(final_data) + geom_point(aes(x=crime_incidents_count, y=unit_price))
# crime_incidents_count vs crime_level
ggplot(final_data) + geom_point(aes(x=crime_incidents_count, y=crime_level))
```
EDA - Bivariate Analysis (Explore the data points with high rating but low price)
```{r}
# unit_price vs avg_rating
ggplot(final_data) + geom_point(aes(x=avg_rating, y=unit_price))
# filter out low price and high rating
LH_data = final_data %>%
  filter(unit_price<=100) %>%
  filter(avg_rating>=5)
summarize_numeric(LH_data)
##### visulaization #####
LH1 = ggplot(LH_data) + geom_histogram(aes(x=crime_level))
LH2 = ggplot(LH_data) + geom_histogram(aes(x=crime_incidents_count))
ggarrange(LH1, LH2, nrow=2)
height <- max(LH_data$latitude) - min(LH_data$latitude)
width <- max(LH_data$longitude) - min(LH_data$longitude)
LA_borders <- c(bottom  = min(LH_data$latitude)  - 0.1 * height, 
                 top     = max(LH_data$latitude)  + 0.1 * height,
                 left    = min(LH_data$longitude) - 0.1 * width,
                 right   = max(LH_data$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = LH_data, mapping = aes(x = longitude, y = latitude))
```

Do clustering based on unit_price
```{r}
train_data = select(final_data, unit_price)
##### elbow diagram #####
wss = function (k) {kmeans(scale(train_data), k, nstart=10)$tot.withinss}
wss_1_10 = map_dbl(1:10, wss) # with k from 1 to 10, means call wss function 10 times to do kmeans
plot(1:10, wss_1_10)
##### kmeans ##### 
res = kmeans(scale(train_data), 3, nstart=25)
final_data_price_cluster = final_data %>% mutate(Cluster = res$cluster)
ggplot(final_data_price_cluster) + geom_bar(aes(x=Cluster))
ggplot(final_data_price_cluster) + geom_count(aes(x=longitude, y=latitude, color=factor(Cluster))) + ylim(33.6, 34.4) + xlim(-118.7, -118.1)
########
# cluster1
cluster1_data = final_data_price_cluster %>%
  filter(Cluster==1)
c1 = ggplot(cluster1_data) + geom_boxplot(aes(x=room_type, y=unit_price))
# cluster2
cluster2_data = final_data_price_cluster %>%
  filter(Cluster==2)
c2 = ggplot(cluster2_data) + geom_boxplot(aes(x=room_type, y=unit_price))
# cluster3
cluster3_data = final_data_price_cluster %>%
  filter(Cluster==3)
c3 = ggplot(cluster3_data) + geom_boxplot(aes(x=room_type, y=unit_price))
ggarrange(c1, c2, c3, nrow=1)
#############
library(ggmap)
height <- max(final_data_price_cluster$latitude) - min(final_data_price_cluster$latitude)
width <- max(final_data_price_cluster$longitude) - min(final_data_price_cluster$longitude)
LA_borders <- c(bottom  = min(final_data_price_cluster$latitude)  - 0.1 * height, 
                 top     = max(final_data_price_cluster$latitude)  + 0.1 * height,
                 left    = min(final_data_price_cluster$longitude) - 0.1 * width,
                 right   = max(final_data_price_cluster$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = final_data_price_cluster, mapping = aes(x = longitude, y = latitude, color=factor(Cluster)))
```
price vs unit_price
```{r}
rp1 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=price)) + ylim(0, 300)
rup1 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=unit_price)) + ylim(0, 150)
ggarrange(rp1, rup1, nrow=1)

```

EDA - availability_365
```{r}
nga1 = ggplot(final_data) + geom_boxplot(aes(x=neighbourhood_group, y=availability_365))
ra1 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=availability_365))
na1 = ggplot(final_data) + geom_boxplot(aes(x=neighbourhood, y=availability_365))
ggarrange(ra1, nga1, nrow=2)
ggplot(final_data) + geom_point(aes(x=availability_365, y=unit_price))
ggplot(final_data) + geom_point(aes(x=availability_365, y=avg_rating))
ggarrange(na1, ra1, nrow=2)

```


EDA - Bivariate Analysis (unit_price)
```{r}
#####
Entire_data = final_data %>%
  filter(room_type=='Entire home/apt')
ggplot(Entire_data) + geom_boxplot(aes(y=unit_price)) + ylim(0, 150)
####
b1 = ggplot(final_data) + geom_boxplot(aes(y=unit_price)) + ylim(0, 500)
ggarrange(b1, b1, nrow=1)
# neighbourhood_group vs. unit_price
np1 = ggplot(final_data) + geom_boxplot(aes(x=neighbourhood_group, y=unit_price))
np2 = ggplot(final_data) + geom_boxplot(aes(x=neighbourhood_group, y=unit_price)) + ylim(0, 150)
ggplot(final_data) + geom_violin(aes(x=neighbourhood_group, y=unit_price)) + ylim(0, 1000)
plot(final_data$neighbourhood_group, join_tb$price, ylim=c(1, 300))

# neighbourhood vs. price
distinct(join_tb, neighbourhood)
ggplot(join_tb) + geom_boxplot(aes(x=neighbourhood, y=price)) + ylim(0, 1000)
ggplot(join_tb) + geom_violin(aes(x=neighbourhood, y=price)) + ylim(0, 300)
plot(join_tb$neighbourhood, join_tb$price, ylim=c(1, 300))

ggplot(join_tb) + geom_boxplot(aes(y=crime_level)) #+ ylim(0, 200)

# room_type vs. unit_price
rp1 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=unit_price))
rp2 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=unit_price)) + ylim(0, 150)
ggarrange(np1, rp1, np2, rp2, nrow=2, ncol=2)
ggplot(final_data) + geom_boxplot(aes(x=room_type, y=unit_price)) + ylim(0, 500)
ggplot(final_data) + geom_violin(aes(x=room_type, y=unit_price)) + ylim(0, 500)

# avg_score vs. price
ggplot(final_data) + geom_point(aes(x=avg_rating, y=price)) + geom_smooth(aes(x=avg_rating, y=price)) + ylim(0, 500)

# avg_score vs. price vs. neighbourhood_group
ggplot(join_tb) + geom_point(aes(x=avg_rating, y=price, color=neighbourhood_group)) + ylim(0, 500)

# avg_score vs. price vs. room_type
ggplot(join_tb) + geom_point(aes(x=avg_score, y=price, color=room_type)) + ylim(0, 500)
```
EDA - Bivariate Analysis (rating)
```{r}
#####
Entire_data = final_data %>%
  filter(room_type=='Entire home/apt')
ggplot(Entire_data) + geom_boxplot(aes(y=unit_price)) + ylim(0, 150)
####
b1 = ggplot(final_data) + geom_boxplot(aes(y=avg_rating))
ggarrange(b1, b1, nrow=1)
# neighbourhood_group vs. unit_price
np1 = ggplot(final_data) + geom_boxplot(aes(x=neighbourhood_group, y=avg_rating))
np2 = ggplot(final_data) + geom_boxplot(aes(x=neighbourhood_group, y=unit_price)) + ylim(0, 150)
ggplot(final_data) + geom_violin(aes(x=neighbourhood_group, y=unit_price)) + ylim(0, 1000)
plot(final_data$neighbourhood_group, join_tb$price, ylim=c(1, 300))

# neighbourhood vs. rating
distinct(join_tb, neighbourhood)
ggplot(join_tb) + geom_boxplot(aes(x=neighbourhood, y=price)) + ylim(0, 1000)
ggplot(join_tb) + geom_violin(aes(x=neighbourhood, y=price)) + ylim(0, 300)
plot(join_tb$neighbourhood, join_tb$price, ylim=c(1, 300))

ggplot(join_tb) + geom_boxplot(aes(y=crime_level)) #+ ylim(0, 200)

# room_type vs. unit_price
rp1 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=avg_rating))
rp2 = ggplot(final_data) + geom_boxplot(aes(x=room_type, y=unit_price)) + ylim(0, 150)
ggarrange(np1, rp1, np2, rp2, nrow=2, ncol=2)
ggplot(final_data) + geom_boxplot(aes(x=room_type, y=unit_price)) + ylim(0, 500)
ggplot(final_data) + geom_violin(aes(x=room_type, y=unit_price)) + ylim(0, 500)

# avg_score vs. price
ggplot(final_data) + geom_point(aes(x=avg_score, y=price)) + geom_smooth(aes(x=avg_score, y=price)) + ylim(0, 500)

# avg_score vs. price vs. neighbourhood_group
ggplot(join_tb) + geom_point(aes(x=avg_rating, y=price, color=neighbourhood_group)) + ylim(0, 500)

# avg_score vs. price vs. room_type
ggplot(join_tb) + geom_point(aes(x=avg_score, y=price, color=room_type)) + ylim(0, 500)
```

Plot all housings unit_price on LA map
```{r}
final_data_roundprice = cbind(final_data)
final_data_roundprice$unit_price =
  round(final_data_roundprice$unit_price, 0)
height <- max(final_data_roundprice$latitude) - min(final_data_roundprice$latitude)
width <- max(final_data_roundprice$longitude) - min(final_data_roundprice$longitude)
LA_borders <- c(bottom  = min(final_data_roundprice$latitude)  - 0.1 * height, 
                 top     = max(final_data_roundprice$latitude)  + 0.1 * height,
                 left    = min(final_data_roundprice$longitude) - 0.1 * width,
                 right   = max(final_data_roundprice$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = final_data_roundprice, mapping = aes(x = longitude, y = latitude, color=unit_price)) + scale_color_distiller(palette = "YlOrRd", direction = 1)
```




Cross table (neighbourhood_group vs room_type)
```{r}
source("http://pcwww.liv.ac.uk/~william/R/crosstab.r") #crosstab
crosstab(final_data, row.vars = "room_type", col.vars = "neighbourhood_group", type = "f")
crosstab(final_data, row.vars = "neighbourhood_group", col.vars = "room_type", type = "f")
library(knitr)
final_data %>% 
  group_by(room_type, neighbourhood_group) %>%
  summarise(count=n()) %>%
  spread(neighbourhood_group, count) #%>%
  kable()
```

Plot all neighbourhood_group on LA map
```{r}
height <- max(final_data$latitude) - min(final_data$latitude)
width <- max(final_data$longitude) - min(final_data$longitude)
LA_borders <- c(bottom  = min(final_data$latitude)  - 0.1 * height, 
                 top     = max(final_data$latitude)  + 0.1 * height,
                 left    = min(final_data$longitude) - 0.1 * width,
                 right   = max(final_data$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = final_data, mapping = aes(x = longitude, y = latitude, color=factor(neighbourhood_group)))
# + scale_color_distiller(palette = "YlOrRd", direction = 1)
```





Plot all room_type on LA map
```{r}
listings_tb = as_tibble(read.csv("./data/listings.csv"))
height <- max(listings_tb$latitude) - min(listings_tb$latitude)
width <- max(listings_tb$longitude) - min(listings_tb$longitude)
LA_borders <- c(bottom  = min(listings_tb$latitude)  - 0.1 * height, 
                 top     = max(listings_tb$latitude)  + 0.1 * height,
                 left    = min(listings_tb$longitude) - 0.1 * width,
                 right   = max(listings_tb$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = listings_tb, mapping = aes(x = longitude, y = latitude, color=factor(room_type)))
# values count
listings_tb %>% 
  group_by(room_type) %>%
  summarise(no_rows = length(room_type))
```

EDA - Bivariate Analysis (Categories vs Measures)
```{r}
distinct(final_data, neighbourhood)
ggplot(final_data) + geom_boxplot(aes(x=neighbourhood, y=unit_price))
ggplot(final_data) + geom_boxplot(aes(x=unit_price, y=neighbourhood))
```

take off the outlier
```{r}
final_data = final_data %>%
  filter(unit_price<1100)
```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```

o
```{r}

```