---
title: "Final project"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

Import all library
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tree)
library(rpart)
library(rpart.plot)
########### data_dict ########### 
data_dict <- function(data, print_table = "No"){
  # packages
  suppressPackageStartupMessages(suppressWarnings(require(tidyverse)))
  suppressPackageStartupMessages(suppressWarnings(require(psych)))
  suppressPackageStartupMessages(suppressWarnings(require(ggpubr)))
  suppressPackageStartupMessages(suppressWarnings(require(gridExtra)))
  # get rid of scientific notation
  options(scipen = 999)
  # Get variable info and NAs
  var_info <- data.frame(Variable = names(data),
                         VariableType = sapply(data, class),
                         MissingValues = sapply(data, function(y) 
                           sum(length(which(is.na(y))))),
                         row.names = NULL)
  # get descriptive stats
  desc_stats <- data.frame(Variable = names(data), 
                           describe(data)[c(2:5, 13, 8:10)], 
                           row.names = NULL)
  # Create the data dictionary
  d_dict <- merge(var_info, desc_stats, by = "Variable")
  d_dict <- d_dict %>% mutate_at(vars("mean":"range"), .fun = round, 2)
  # NA's for summary stats of variables not of class numeric or integer
  d_dict <- d_dict %>%
    mutate(mean = ifelse(VariableType == "numeric" | VariableType == "integer", mean, ""),
           sd = ifelse(VariableType == "numeric" | VariableType == "integer", sd, ""),
           median = ifelse(VariableType == "numeric" | VariableType == "integer", median, ""),
           se = ifelse(VariableType == "numeric" | VariableType == "integer", se, ""),
           min = ifelse(VariableType == "numeric" | VariableType == "integer", min, ""),
           max = ifelse(VariableType == "numeric" | VariableType == "integer", max, ""),
           range = ifelse(VariableType == "numeric" | VariableType == "integer", range, ""))
  # return the result
  if(print_table == "No"){
    return(d_dict)
  } else {
    #create table if table = TRUE
    d_dict <- ggtexttable(d_dict,
                          rows = NULL)
    return(d_dict)
  }
}

########### summarize_numeric ########### 
summarize_numeric = function(dataset) {

  dataset = select_if(dataset, is.numeric)
  summary.table = data.frame(Attribute = names(dataset))

  summary.table = summary.table %>%
    mutate('Missing Values' = apply(dataset, 2, function (x) sum(is.na(x))),
           'Unique Values' = apply(dataset, 2, function (x) length(unique(x))),
           'Mean' = colMeans(dataset, na.rm = TRUE),
           'Min' = apply(dataset, 2, function (x) min(x, na.rm = TRUE)),
           'Max' = apply(dataset, 2, function (x) max(x, na.rm = TRUE)),
           'SD' = apply(dataset, 2, function (x) sd(x, na.rm = TRUE))
    )
  summary.table
}
```

Read final jointed table
```{r}
# final_data = as_tibble(read.csv("./data/all_jointed_data.csv"))
final_data = as_tibble(read.csv("./data/all_data_v3.csv"))
ggplot(final_data) + geom_bar(aes(x=neighbourhood_group)) 
# data_dict(final_data, print_table = 'Yes')
```

convert price into unit price (price/room_type)
```{r}
# 4, 2, 2, 1
final_data = final_data %>%
  mutate(unit_price = ifelse(room_type=='Entire home/apt',price/4,ifelse(room_type=='Shared room',price,price/2)))
# drop outlier
final_data = final_data %>%
  filter(unit_price<1100)

```



one-hot-encode room_type and neighbourhood
(https://community.rstudio.com/t/factor-to-one-hot-encoding-aka-dummy-variables-using-logicals/69236/2)
```{r}
final_data_OHE = final_data %>%
  mutate(n = 1) %>% 
  pivot_wider(names_from = neighbourhood_group, values_from=n, values_fill=0) %>%
  mutate(n = 1) %>% 
  pivot_wider(names_from = room_type, values_from=n, values_fill=0)
```

Group by neighborhood and average on the other attributes
```{r}
final_data_OHE %>% filter(neighbourhood=='Hollywood Hills')
grouped_neighbourhood_data = final_data_OHE %>%
                                group_by(neighbourhood) %>% 
                                summarise(shared_room_count = sum(`Shared room`),
                                          private_room_count = sum(`Private room`),
                                          Entire_home_apt_count = sum(`Entire home/apt`),
                                          Hotel_room_count = sum(`Hotel room`),
                                          avg_unit_price = mean(unit_price),
                                          avg_crime_level = mean(crime_level),
                                          avg_crime_incidents_count = mean(crime_incidents_count),
                                          avg_rating = mean(avg_rating),
                                          latitude = mean(latitude),
                                          longitude = mean(longitude),
                                          housing_count = n()
                                          )

```
summarize the new grouping df
```{r}
# data_dict
data_dict(grouped_neighbourhood_data, print_table = 'Yes')
# summarize_numeric
numeric_data = grouped_neighbourhood_data %>% select(avg_unit_price, avg_rating, avg_crime_level, avg_crime_incidents_count, shared_room_count, 	private_room_count, Entire_home_apt_count, Hotel_room_count)
summarize_numeric(numeric_data)
summarize_numeric(grouped_neighbourhood_data)
```


Plot avg_unit_price neighbourhood in LA map
```{r}
grouped_neighbourhood_data_roundprice = cbind(grouped_neighbourhood_data)
grouped_neighbourhood_data_roundprice$avg_unit_price =
  round(grouped_neighbourhood_data_roundprice$avg_unit_price, 0)
height <- max(grouped_neighbourhood_data$latitude) - min(grouped_neighbourhood_data$latitude)
width <- max(grouped_neighbourhood_data$longitude) - min(grouped_neighbourhood_data$longitude)
LA_borders <- c(bottom  = min(grouped_neighbourhood_data$latitude)  - 0.1 * height, 
                 top     = max(grouped_neighbourhood_data$latitude)  + 0.1 * height,
                 left    = min(grouped_neighbourhood_data$longitude) - 0.1 * width,
                 right   = max(grouped_neighbourhood_data$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = grouped_neighbourhood_data_roundprice, mapping = aes(x = longitude, y = latitude, color=factor(avg_unit_price), size=avg_unit_price))
```


exclude unimportant attributes 
```{r}
train_data = select(grouped_neighbourhood_data, -c(neighbourhood, housing_count, latitude, longitude))
```

Correlation matrix
```{r}
# install.packages("ggcorrplot")
library(ggcorrplot)
# cor_data = select(final_data, c(unit_price, availability_365, avg_rating, crime_level, crime_incidents_count))
fullCorrMatrix = round(cor(train_data %>% select_if(is.numeric)), 2)
ggcorrplot(fullCorrMatrix, lab = TRUE)
```



Elbow diagram
```{r}
wss = function (k) {kmeans(scale(train_data), k, nstart=10)$tot.withinss}
wss_1_10 = map_dbl(1:10, wss) # with k from 1 to 10, means call wss function 10 times to do kmeans
plot(1:10, wss_1_10)
```
Look at a clustering with k = 3
```{r}
res = kmeans(scale(train_data), 3, nstart=25)
grouped_neighbourhood_data_res = grouped_neighbourhood_data %>% mutate(Cluster = res$cluster)
ggplot(grouped_neighbourhood_data_res) + geom_bar(aes(x=Cluster)) 
```


summarise for each cluster
```{r}
# summarize_numeric = function(dataset) {
#   
#   dataset = select_if(dataset, is.numeric)
#   summary.table = data.frame(Attribute = names(dataset))
#   
#   summary.table = summary.table %>% 
#     mutate('Missing Values' = apply(dataset, 2, function (x) sum(is.na(x))),
#            'Unique Values' = apply(dataset, 2, function (x) length(unique(x))),
#            'Mean' = colMeans(dataset, na.rm = TRUE),
#            'Min' = apply(dataset, 2, function (x) min(x, na.rm = TRUE)),
#            'Max' = apply(dataset, 2, function (x) max(x, na.rm = TRUE)),
#            'SD' = apply(dataset, 2, function (x) sd(x, na.rm = TRUE))
#     )
#   summary.table
# }
########## cluster1 #############
grouped_neighbourhood_data_res %>%
  filter(Cluster==1) %>%
  summarize_numeric()
########## cluster2 #############
grouped_neighbourhood_data_res %>%
  filter(Cluster==2) %>%
  summarize_numeric()
########## cluster3 #############
grouped_neighbourhood_data_res %>%
  filter(Cluster==3) %>%
  summarize_numeric()
```

o
```{r}
library(ggplot2)  # The grammar of graphics package
library(maps)     # Provides latitude and longitude data for various maps
```

o
```{r}
# ggplot(test1) + geom_point(aes(x=avg_severity_level, y = price, color=factor(Cluster), shape=factor(Cluster)))
# ggplot(train_data_res) + geom_count(aes(x=longitude, y = latitude, color=factor(Cluster))) + ylim(33.6, 34.4) + xlim(-118.1, -118.7)
# original
# ggplot(train_data_res) + geom_count(aes(x=longitude, y = latitude)) + ylim(33.6, 34.4) + xlim(-118.1, -118.7)
# ggplot(test1) + geom_histogram(aes(x=price)) + xlim(0,1000)
# test1 = test1 %>%
#   mutate(price_level = ifelse(price<=100,0,ifelse(price>200,2,1)))
# ggplot(test1) + geom_bar(aes(x=price_level)) 
# ggplot(test1) + geom_count(aes(x=longitude, y = latitude, color=factor(price_level))) + ylim(33.6, 34.4) + xlim(-118.1, -118.7)
```

o
```{r}
# MainStates <- map_data("county", region = 'california')
# ggplot() + 
#   geom_polygon( data=MainStates, aes(x=long, y=lat, group=group),
#                 color="black", fill="lightyellow" )
```

Plot on LA map
https://rstudio-pubs-static.s3.amazonaws.com/434852_bb92f97f268148a9b963754d8dc5d95a.html
```{r}
# install.packages('ggmap')
library(ggmap)
height <- max(grouped_neighbourhood_data$latitude) - min(grouped_neighbourhood_data$latitude)
width <- max(grouped_neighbourhood_data$longitude) - min(grouped_neighbourhood_data$longitude)
LA_borders <- c(bottom  = min(grouped_neighbourhood_data$latitude)  - 0.1 * height, 
                 top     = max(grouped_neighbourhood_data$latitude)  + 0.1 * height,
                 left    = min(grouped_neighbourhood_data$longitude) - 0.1 * width,
                 right   = max(grouped_neighbourhood_data$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = grouped_neighbourhood_data_res, mapping = aes(x = longitude, y = latitude, color=factor(Cluster), size=housing_count))
```
#########################################################################################################

Whole
```{r}
train_DT = select(grouped_neighbourhood_data_res, -c(neighbourhood))
regr_tree= tree(factor(Cluster) ~ .-Cluster, data=train_DT) 
plot(regr_tree); text(regr_tree, pretty=0)
######
rpart.plot(rpart(Cluster~., data = train_DT, method = "class"), tweak = 1, type = 5, main = "All neighbourhoods: Decision Tree")
```
Classify price into five level(0~100~200~300~400+) 
```{r}
grouped_neighbourhood_data_res = grouped_neighbourhood_data_res %>%
  mutate(price_level = ifelse(avg_unit_price<100,1,ifelse(avg_unit_price<200,2,ifelse(avg_unit_price<300,3,ifelse(avg_unit_price<400,4,5)))))

```

cluster 1 DT
```{r}
data_c1 = grouped_neighbourhood_data_res %>%
  filter(Cluster==1)
train_DT = select(data_c1, -c(neighbourhood))
regr_tree= tree(avg_unit_price ~ .-avg_unit_price, data=data_c1) 
plot(regr_tree); text(regr_tree, pretty=0)
##################3

rpart.plot(rpart(price_level~.-price_level, data = data_c1, method = "class"), tweak = 1, type = 5, main = "Cluater1(high housing rented, high criminal incidentss): Decision Tree")
```

cluster 2 DT
```{r}
data_c2 = grouped_neighbourhood_data_res %>%
  filter(Cluster==2)
train_DT = select(data_c2, -c(neighbourhood))
regr_tree= tree(avg_unit_price ~ .-avg_unit_price-price_level, data=data_c2) 
plot(regr_tree); text(regr_tree, pretty=0)
####
rpart.plot(rpart(price_level~.-price_level, data = data_c2, method = "class"), tweak = 1, type = 5, main = "Cluater2(low crime incidents, high unit price): Decision Tree")
```

cluster 3 DT
```{r}
data_c3 = grouped_neighbourhood_data_res %>%
  filter(Cluster==3)
train_DT = select(data_c3, -c(neighbourhood))
regr_tree= tree(avg_unit_price ~ .-avg_unit_price, data=data_c3) 
plot(regr_tree); text(regr_tree, pretty=0)
######
rpart.plot(rpart(avg_unit_price~.-avg_unit_price, data = data_c2, method = "class"), tweak = 1, type = 5, main = "Cluater3(low housing rented): Decision Tree")
```
#########################################################################################################
#########################################################################################################
(Only include cities of LA)
Group by neighborhood and average on the other attributes
```{r}
final_data_OHE = final_data %>%
  mutate(n = 1) %>% 
  pivot_wider(names_from = room_type, values_from=n, values_fill=0)

final_data_OHE_LA = final_data_OHE %>%
  filter(neighbourhood_group=='City of Los Angeles')

# final_data_OHE_LA %>% filter(neighbourhood=='Hollywood Hills')
grouped_neighbourhood_LA = final_data_OHE_LA %>%
                                group_by(neighbourhood) %>% 
                                summarise(shared_room_count = sum(`Shared room`),
                                          private_room_count = sum(`Private room`),
                                          Entire_home_apt_count = sum(`Entire home/apt`),
                                          Hotel_room_count = sum(`Hotel room`),
                                          avg_unit_price = mean(unit_price),
                                          avg_crime_level = mean(crime_level),
                                          avg_crime_incidents_count = mean(crime_incidents_count),
                                          avg_rating = mean(avg_rating),
                                          latitude = mean(latitude),
                                          longitude = mean(longitude),
                                          housing_count = n())
train_data = select(grouped_neighbourhood_LA, -c(neighbourhood, housing_count, latitude, longitude))
```

o
```{r}
fullCorrMatrix = round(cor(train_data %>% select_if(is.numeric)), 2)
ggcorrplot(fullCorrMatrix, lab = TRUE)
```

o
```{r}
wss = function (k) {kmeans(scale(train_data), k, nstart=10)$tot.withinss}
wss_1_10 = map_dbl(1:10, wss) # with k from 1 to 10, means call wss function 10 times to do kmeans
plot(1:10, wss_1_10)
```

o
```{r}
res = kmeans(scale(train_data), 3, nstart=25)
grouped_neighbourhood_data_res = grouped_neighbourhood_LA %>% mutate(Cluster = res$cluster)
ggplot(grouped_neighbourhood_data_res) + geom_bar(aes(x=Cluster)) 
```

o
```{r}
########## cluster1 #############
grouped_neighbourhood_data_res %>%
  filter(Cluster==1) %>%
  summarize_numeric()
########## cluster2 #############
grouped_neighbourhood_data_res %>%
  filter(Cluster==2) %>%
  summarize_numeric()
########## cluster3 #############
grouped_neighbourhood_data_res %>%
  filter(Cluster==3) %>%
  summarize_numeric()
```

o
```{r}
height <- max(grouped_neighbourhood_LA$latitude) - min(grouped_neighbourhood_LA$latitude)
width <- max(grouped_neighbourhood_LA$longitude) - min(grouped_neighbourhood_LA$longitude)
LA_borders <- c(bottom  = min(grouped_neighbourhood_LA$latitude)  - 0.1 * height, 
                 top     = max(grouped_neighbourhood_LA$latitude)  + 0.1 * height,
                 left    = min(grouped_neighbourhood_LA$longitude) - 0.1 * width,
                 right   = max(grouped_neighbourhood_LA$longitude) + 0.1 * width)
 
map <- get_stamenmap(LA_borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
    geom_point(data = grouped_neighbourhood_data_res, mapping = aes(x = longitude, y = latitude, color=factor(Cluster), size=housing_count))
```

o
```{r}

```